Tulai

### 2025-07-28 paper/paper.qmd
map revised
stash
Save local changes before merging

library(ggmap) # devtools::install_github("stadiamaps/ggmap")
library(ggmap)
ggmap::register_stadiamaps(key = "ca45118a-734f-480b-8c3c-8d82e5a361e3")

@@

ggsave(here::here("figures/site-map.png"),
       width = 4.45,
       height = 4.75,
       units = "in", 
       dpi = 300
       )

>>>>

library(ggmap) # devtools::install_github("stadiamaps/ggmap")
ggmap::register_stadiamaps(key = "ca45118a-734f-480b-8c3c-8d82e5a361e3")

@@

ggsave(here::here("figures/site-map.png"),
       width = 4.45,
       height = 4.75,
       units = "in", 
       dpi = 600
       )
